Notes for Week of 12/24/18 - 12/31/18

### 2019-01-30 notes/weekly_notes/12.31.18.NotesForWeek.tex
added backlog of notes

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}

@@

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

@@

We are given two unknown distributions, $P$ and $Q$, both supported on $D \subset \Rd$, with continuous density functions $p$ and $q$, respectively. We have the capacity to sample from either distribution. Our goal is to test the nonparametric hypothesis $H_0: P = Q$ vs. the alternative $H_1: P \neq Q$.

Under the \textbf{binomial data model}, we sample data $\set{z_1, \ldots, z_n}$ as follows. For each $i$, we draw an independent Rademacher label $\ell_i \in \set{1, -1}$, $\mathbb{P}(\ell_i = 1) = \mathbb{P}(\ell_i = -1) = 1/2$. Then, if $\ell_i = 1$ we sample $z_i \sim P$, whereas if $\ell_i = -1$ we samle $z_i \sim Q$ otherwise. Define $1_X$ to be the length $n$ indicator vector for $\ell_i = 1$
\begin{equation*}
1_X(i) = 
\begin{cases}
1, \ell_i = 1\\
0 \text{ otherwise } 
\end{cases}
\end{equation*}
and similarly for $1_Y$
\begin{equation*}
1_Y(i) = 
\begin{cases}
1, \ell_i= -1 \\
0 \text{ otherwise } 
\end{cases}
\end{equation*}
Denote the number of positive labels $N = \sum_{i = 1}^{n} 1_x(i)$, and let $M$ be such that $n = N + M$. Then, let the \textbf{normalized label vector} $a$ be given by $a = \frac{1}{N}1_X - \frac{1}{M} 1_Y$.

@@

Heuristically, our graph based test will attempt to identify whether samples from the same distribution are on average more similar than samples from different distributions. As a result, we introduce $K$, a \textbf{kernel function} which measures similarity, and make the following assumptions on $K$
\begin{itemize}
	\item $K: [0,\infty) \to [0,\infty)$ is non-increasing.
	\item The integral $\int_{0}^{\infty} K(r) r^d dr$ is finite.
\end{itemize}

@@

To relate the risk functional of (\ref{eqn: empirical_risk_functional}) to the variational problem of (\ref{eqn: laplacian_smooth_statistic}), we introduce the \textbf{constrained empirical risk functional}, $R_n^{(con)}(u_n)$, defined by
\begin{equation*}
R_n^{(con)}(u_n) := 
\begin{cases}
R_n(u_n), \text{ if $\mathcal{E}_n^2(u_n) \leq 1$} \\
\infty, \text{ otherwise }
\end{cases}
\end{equation*}
where $\mathcal{E}_n^2(u_n)$ is the \textbf{Laplacian regularization functional} given by
\begin{equation*}
\mathcal{E}_n^2(u_n) \defeq \frac{1}{n^2 \epsilon_n^{d+1}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} K\left(\frac{\norm{z_i - z_j}}{\epsilon_n}\right)(u_n(z_i) - u_n(z_j))^2.
\end{equation*}

@@

\begin{proof}[Proof attempt of Theorem \ref{thm: consistency_of_empirical_risk_minimizer}]

We begin by restricting ourselves to the case where $\underset{n \to \infty}{\limsup}~ \E_n^2(u_n^{\star}) \leq 1$.
As a result of Lemma 
\end{proof}
\subsection{Technical results.}

>>>>

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\text{vol}}
\newcommand{\Bal}{\textrm{Bal}}
\newcommand{\Cut}{\textrm{Cut}}
\newcommand{\Ind}{\textrm{Ind}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\Perp}{\perp \! \! \! \perp}
\newcommand{\Naturals}{\mathbb{N}}

@@

%%% Set related notation
\newcommand{\Dset}{\mathcal{D}}

%%% Distribution related notation
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Qbb}{\mathbb{Q}}
% \newcommand{\Pr}{\mathrm{Pr}}}

%%% Functionals
\newcommand{\1}{\mathbf{1}}
\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

@@

We are given two unknown distributions, $\Pbb$ and $\Qbb$, both supported on \textcolor{red}{$D \subset \Rd$}, with \textcolor{red}{continuous} density functions $p$ and $q$, respectively. We have the capacity to sample from either distribution. Our goal is to test the nonparametric hypothesis $H_0: \Pbb = \Qbb$ vs. the alternative $H_1: \Pbb \neq \Qbb$.

Under the \emph{binomial data model}, we sample data $\set{z_1, \ldots, z_n}$ as follows: for $i = 1,\ldots,n$, we draw an independent Rademacher label $\ell_i \in \set{1, -1}$, $\Pr(\ell_i = 1) = \Pr(\ell_i = -1) = 1/2$. Then, if $\ell_i = 1$ we sample $z_i \sim \Pbb$, whereas if $\ell_i = -1$ we sample $z_i \sim \Qbb$. Define $\1_X$ to be the length $n$ indicator vector for $\ell_i = 1$
\begin{equation*}
\1_X(i) = 
\begin{cases}
1, \ell_i = 1\\
0 \text{ otherwise } 
\end{cases}
\end{equation*}
and similarly for $\1_Y$
\begin{equation*}
\1_Y(i) = 
\begin{cases}
1, \ell_i= -1 \\
0 \text{ otherwise } 
\end{cases}
\end{equation*}
Denote the number of positive labels $N = \sum_{i = 1}^{n} \1_X(i)$, for $M$ the number of negative labels we have $n = N + M$. Then the \emph{normalized label vector} $a$ is given by $a = \frac{1}{N}\1_X - \frac{1}{M}\1_Y$.

@@

Heuristically, our graph-based test will attempt to identify whether samples from the same distribution are on average more similar than samples from different distributions. As a result, we introduce $K$, a \textbf{kernel function} which measures similarity, and make the following assumptions on $K$
\begin{itemize}
	\item $K: [0,\infty) \to [0,\infty)$ is non-increasing.
	\item The integral $\int_{0}^{\infty} K(r) r^d dr$ is finite.
\end{itemize}

@@

To relate the risk functional of (\ref{eqn: empirical_risk_functional}) to the variational problem of (\ref{eqn: laplacian_smooth_statistic}), we introduce the \textbf{constrained empirical risk functional}, $R_n^{(con)}(u_n)$, defined by
\begin{equation*}
R_n^{(con)}(u_n) := 
\begin{cases}
R_n(u_n), \text{ if $\mathcal{E}_n^2(u_n) \leq 1$} \\
\infty, \text{ otherwise }
\end{cases}
\end{equation*}
where $\mathcal{E}_n^2(u_n)$ is the \textbf{Laplacian regularization functional} given by
\begin{equation*}
\mathcal{E}_n^2(u_n) \defeq \frac{1}{n^2 \epsilon_n^{d+2}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} K\left(\frac{\norm{z_i - z_j}}{\epsilon_n}\right)(u_n(z_i) - u_n(z_j))^2.
\end{equation*}

@@

\begin{proof}[Proof of Theorem \ref{thm: consistency_of_empirical_risk_minimizer}]
	We know $\E_{\infty}^2(u^{\star}) \leq 1$ (otherwise $R^{(con)}(0) = 0 \leq R^{(con)}(u^{\star})$)

	By Lemma \ref{thm: garciatrillos17}, we have that there exists some $u_n \overset{TL^2}{\to} u^{\star}$ such that
	\begin{equation*}
	\limsup_{n \to \infty} \E_n^2(u_n) \leq \E_{\infty}^2(u^{\star}) \leq 1
	\end{equation*}
	and therefore by Lemma \ref{lem: conv_of_risk_functional}
	\begin{equation*}
	\limsup_{n \to \infty} R_n(u_n) = R(u^{\star})
	\end{equation*}
	Of course, we do not know that $\E_n^2(u_n) \leq 1$, and so we do not know that the $R_n^{(con)}(u_n) < \infty$, even in the limit. However, taking $u_n' = u_n \cdot \left(\max\{1, \E_n^2(u_n) \}\right)^{-1}$, we have $\E_n^2(u_n') \leq 1$. Moreover,
	\begin{align}
	\label{eqn: theorem_consistency_1}
	\lim_{n \to \infty} R_n(u_n') & = \lim_{n \to \infty} \frac{R_n(u_n)}{\bigl(\max\left\{1, \E_n^2(u_n)\right\}\bigr)} \nonumber \\
	& = R(u^{\star})
	\end{align}
	where the latter equality follows from the continuous mapping theorem. 
	Since
	\begin{equation*}
	 R_n(u_n^{\star}) \leq R_n^{(con)}(u_n^{\star}) \leq R_n^{(con)}(u_n') = R_n(u_n')
	\end{equation*}
	we have
	\begin{equation*}
	\lim_{n \to \infty} R_n(u_n^{\star}) \leq R(u^{\star}).
	\end{equation*}

	Finally, the above reasoning implies
	\begin{equation*}
	\lim_{n \to \infty} R_n^{(con)}(u_n^{\star}) \leq R(u^{\star}) < \infty. 
	\end{equation*}
	As a result, clearly
	\begin{equation*}
	\limsup_{n \to \infty} \E_n^2(u_n^{\star}) \leq 1 < \infty 
	\end{equation*}
	and so by Theorem \ref{thm: garciatrillos17}, we have that every subsequence of $u_n^{\star}$ is $TL^2$ convergent. As a result, 
	\begin{equation*}
	\liminf_{n \to \infty} \E_n^2(u_n^{\star}) \geq \inf_{u \in L^2(\nu)} R(u) = R(u^{\star})
	\end{equation*}
	and so we have shown
	\begin{equation*}
	\lim_{n \to \infty} R_n(u_n^{\star}) = R(u^{\star}).
	\end{equation*}
\end{proof}
\subsection{Technical results.}

\begin{theorem}[\textcolor{red}{Garcia-Trillos 17}]
	\label{thm: garciatrillos17}
	Let $d \geq 2$ and let $\Dset \subset \Rd$ be an open, bounded, connected set with Lipschitz boundary. Let $\mu$ be a probability measure on $\Dset$ with continuous density $\rho$, satisfying 
	\begin{equation*}
	m \leq \rho(x) \leq M \tag{$\forall x \in D$}
	\end{equation*}
	for some $0 < m \leq M$. Let $z_1, \ldots, z_n$ be a sequence of i.i.d random points chosen according to $\mu$. Let $(\epsilon_n)$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{align*}
	& \lim_{n \to \infty} \frac{(\log n)^{3/4}}{n^{1/2}} \frac{1}{\epsilon_n} = 0 ~~ \text{if $d = 2$} \\
	& \lim_{n \to \infty} \frac{(\log n)^{1/d}}{n^{1/d}} \frac{1}{\epsilon_n} = 0 ~~ \text{if $d \geq 3$}
	\end{align*}
	Assume the kernel $K$ satisfies conditions: 
	\begin{align*}
	& K(0) > 0 \text{and $K$ is continuous at $0$.} \tag{\textbf{K1}} \\
	& K \text{is non-increasing.} \tag{\textbf{K2}} \\
	& \text{The integral $\int_{0}^{\infty} K(r) r^{d+1} dr$ is finite.} \tag{\textbf{K3}}
	\end{align*}
	Then, with probability one, the following statement holds:
	\begin{equation*}
	\E_n^2(u_n) \overset{\Gamma}{\to} \E_{\infty}^2(u)
	\end{equation*}
	in the $TL^2$ sense.

	Moreover, every sequence $(u_n)$ with $u_n \in L^2(\mu_n)$ for which
	\begin{align*}
	\sup_{n \in \Naturals} \norm{u_n}_{\mu_n} & < \infty \\
	\sup_{n \in \Naturals} \E_n^2(u_n) & < \infty
	\end{align*}
	is pre-compact in $TL^2$.
\end{theorem}
